---
title: "Assignment - Week 10"
author: "Evan McLaughlin"
date: "4/17/2021"
output:
  pdf_document: default
  html_document: default
---

## Overview

Get the primary example code from Chapter 2 of Text Mining with R working and provide a citation for this base code.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidytext)
library(tidyr)
library(tidyverse)
library(textdata)
library(NLP)
library(ggplot2)
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

```

## Intro

First, let's take a look at the sentiment analysis conducted in Chapter 2 of Text Mining with R: 

## Robinson, David & Silge, Julia. (2017). Text Mining with R: A Tidy Approach. O’Reilly Media. https://www.tidytextmining.com/sentiment.html
```{r}
library(janeaustenr)
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)

# I've thus assigned a word per row in this dataset, and now I can attempt some sentiment analysis. 

nrc_joy <- get_sentiments("nrc") %>%
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)

```
```{r}
library(tidyr)

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```
```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice

```

```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```
Next we can distill the dataset to the most common positive and negative words
```{r}
get_sentiments("nrc") %>%
  filter(sentiment %in% c(
    "positive",
    "negative"
  )) %>%
  count(sentiment)

get_sentiments("bing") %>%
  count(sentiment)

bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
bing_word_counts
```
Lastly, let's look at it graphically

```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(
    y = "Contribution to sentiment",
    x = NULL
  ) +
  coord_flip()
```
```{r}
# Let's filter out the stop words and produce a word cloud
custom_stop_words <- bind_rows(
  tibble(
    word = c("miss"),
    lexicon = c("custom")
  ),
  stop_words
)

#custom_stop_words
library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))


```
Next we can discern between positive or negative words in our wordcloud

```{r}
library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)

```
Let's look at the units beyond words
```{r}

p_and_p_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")

p_and_p_sentences$sentence[2]
#> [1] "by jane austen"

austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())
#> # A tibble: 6 x 2
#>   book                chapters
#>   <fct>                  <int>
#> 1 Sense & Sensibility       51
#> 2 Pride & Prejudice         62
#> 3 Mansfield Park            49
#> 4 Emma                      56
#> 5 Northanger Abbey          32
#> 6 Persuasion                25

```

## New Corpus

This dataset comes from kaggle and is a collection of customer sentiment pulled from Rotten Tomatoes. It includes language from the most popular review for each movie. 

```{r rotten tomatoes}

reviews <- read.csv("https://raw.githubusercontent.com/evanmclaughlin/ECM607/master/RT_movie_reviews.csv")

head(reviews)
```


```{r}
# I'm going to remove some columns and retain the data that I really want to use for sentiment analysis
dataset <- subset(reviews, select = c(movie_title, critics_consensus))

head(dataset) 
```

First, I'll tokenize the critics' consensus  
```{r}
token <- dataset %>%
  unnest_tokens(word, 2) %>%
  anti_join(stop_words)

token_count <- token %>%
  count(word) %>%
  arrange(desc(n))

head(token_count)

```
There are some words at the top here that don't add much to our analysis, so I'll customize my stop word list to improve the analysis.
```{r}
new_stop <- data.frame(word = c("story", "cast", "performance","performances", "director", "movie", "film", "life", "offers", "makes", "characters", "fans", "viewers", "genre", "direction", "writer", "script", "tale", "ultimately", "material", "effects", "character", "time", "subject", "features", "title", "plot", "comedy", "drama", "thriller", "action", "horror", "acted", "premise"), lexicon = "custom")
my_stopwords <- rbind(new_stop, stop_words)

critic <- token %>%
  filter(!word %in% my_stopwords$word)

critic_count <- critic %>%
  count(word, sort = TRUE)

head(critic_count)
```

That's a pretty good collection of sentiment. Let's introduce a lexicon to bucket the sentiments as either positive or negative.
```{r}
get_sentiments("bing")
```
```{r}
# I'll now run my sentiment dataset against bing
critic_bing_pct <- critic %>% 
  inner_join(get_sentiments("bing")) %>%
  filter(sentiment %in% c(
    "positive",
    "negative"
  )) %>%
  count(sentiment) %>%
  mutate(total = n / sum(n))

critic_bing_pct
```
This is especially surprising. The critics' job is criticism after all. Let's take a look at this graphically.

```{r}
bing_word_counts <- critic %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

```
Pretty strange that bing buckets "funny" as a negative, and it's especially a shame that it contributes disproportionately to the negative sentiment, but our analysis at least highlights a problem with using bing for movie review purposes!

